% Paper 11 of The Windstorm Institute (Track 2: Entropic Bounds)
\documentclass[12pt,a4paper]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{booktabs}

\title{Gravitational Entropy Escrow: An Interpretive Synthesis of Thermodynamic Approaches to Gravity}

\author{Grant Lavell Whitmer III\\
The Windstorm Institute, Fort Ann, NY 12827, USA\\
\texttt{grantwhitmer3@gmail.com}}

\date{May 2026}

\begin{document}

\maketitle

\begin{abstract}
We propose a physical reframing under which gravity and entropy are revealed as the same phenomenon viewed through different vocabularies. Gravitational binding energy is entropy held in escrow against the local Unruh temperature: bound mass-pairs hold entropy off the books, and the universe attracts because the books want to balance. Escape velocity is the threshold at which sufficient compensating entropy can be produced to redeem the escrow. The equivalence principle is the statement that escrow gradients are observer-relative the same way entropy is observer-relative, with tidal forces emerging as the irreducible piece that survives transformation to a free-fall frame. Black holes are the limiting case in which escrow becomes infinite and is forced to manifest directly as horizon area, recovering Bekenstein--Hawking entropy as a structural consequence rather than a separate result. The mathematical machinery underlying the reframing is due to Bekenstein, Hawking, Unruh, Jacobson, Padmanabhan, Verlinde, and van Putten; we claim no priority on individual derivations. What is offered here is the picture that connects them: universal attractiveness, the impossibility of shielding, the second-law character of gravitational binding, the area-law of black hole entropy, and the recovery of Newton's law and of the order of magnitude and universality of the empirical Milgrom acceleration scale $a_0$ all follow from one principle. We sketch a covariant extension and engage honestly with the empirical literature, including the constraints on cosmological evolution of $a_0$ established by Milgrom (2017) and the radial-profile pattern of cluster mass discrepancies, both of which any framework in this family must accommodate.
\end{abstract}

\noindent\textbf{Keywords:} entropic gravity; emergent gravity; thermodynamics of spacetime; Bekenstein--Hawking entropy; Unruh temperature; MOND; Milgrom acceleration scale; Verlinde gravity; equivalence principle; foundations of physics.

\section{Introduction}

The full text of this paper (current version v0.6.11) is provided as \texttt{paper.pdf} in this repository. The markdown source is in \texttt{paper/Paper11-v0.6.11-draft.md}.

\section*{Code and Data Availability}

The Python analysis scripts used to produce the SPARC reanalysis (\S8.4) and the interpolation comparison (\S10), and the Genzel five-case test (\S6.1), will be archived at \url{https://github.com/Windstorm-Labs/gravitational-entropy-escrow}. The full SPARC mass-models table (Lelli, McGaugh \& Schombert 2016) is publicly available from the SPARC project at \url{http://astroweb.cwru.edu/SPARC/}. The deposited code reproduces the numerical experiments reported in Sections 6.1, 8.4, and 10 of the paper. Reproducibility instructions and dependency lists are in the deposited README.

\end{document}
